Developing a preprint culture in biology

### 2013-02-26 ms.tex
Fixing spelling error

The ongoing discussions on the scientific publication process, peer-review and
alternative publication models are all symptoms of the current uneasiness with
the ever growing obsession with bibliographic metrics such as the impact factor
\cite{Fisher2012}. Researchers are pressured to orient their publication
strategy to maximize their number of publications and total citations. A
well-known consequence is the initial submition of manuscripts to the most
prestigious journals, followed by resubmission to progressively ``lower level''
journals as they are rejected. The numerous negative impacts of such behavior
have been discussed in depth \cite{hoc09} and include a long delay between the
time a manuscript is finished and its publication. Research activities and the
publication process are drifting away from their fundamental objective, namely
the distribution of novel scientific discoveries.

>>>>

The ongoing discussions on the scientific publication process, peer-review and
alternative publication models are all symptoms of the current uneasiness with
the ever growing obsession with bibliographic metrics such as the impact factor
\cite{Fisher2012}. Researchers are pressured to orient their publication
strategy to maximize their number of publications and total citations. A
well-known consequence is the initial submission of manuscripts to the most
prestigious journals, followed by resubmission to progressively ``lower level''
journals as they are rejected. The numerous negative impacts of such behavior
have been discussed in depth \cite{hoc09} and include a long delay between the
time a manuscript is finished and its publication. Research activities and the
publication process are drifting away from their fundamental objective, namely
the distribution of novel scientific discoveries.
